\vspace{-2.0cm} \textbf{Talking with signs} \\ \Large \textbf{A method for progressively detect sings in a non annotated Peruvian Sings Language corpus}

### 2019-11-20 article/article-tesis.tex
adding article updates

\title{%
	\vspace{-2.0cm}
	\textbf{Talking with signs} \\	
	\Large \textbf{A method for detecting signs in a weakly annotated dataset}
}

@@

\begin{abstract}
People with deafness or hearing disabilities who aim to use computer based systems, state of art video classification and human action recognition rely in a combination of traditional and new methods like optical flow and 3D CNN. In this article we show a novel method to detect Peruvian Sign Language elements (nSDm) from a weakly annotated videos dataset. Video annotation techniques were applied increasing the models performance, as a result we achieved XX precision and XX exhaustiveness by training a 3D CNN with optical flow inputs.   \\
\keywords{video classification,human actions detection, optical flow, 3D CNN.}
\end{abstract}

\section{Introduction}\label{intro}

The World Health Organization (WHO) stated that 466 million people world wide have disabling hearing loss, estimating that by 2050 over 900 million people will have disabling hearing loss and will represent a global cost of 750 million dollars annually \cite{deafness_and_hearing_loss_2019}.

The Peruvian Institute of Informatics and Statistics (INEI) conducted a national disabilities survey with the objective of segmenting and better understanding which disabilities affect the Peruvian population \cite{disabilities_survey_2012}, the results showed that 1.8\% of the Peruvian population suffer at least partial when not permanent deafness or hearing limitation.

As of today, thanks to deep learning models for computer vision and natural language processing, it is completely feasible to propose systems able to detect and transcribe sign languages. However, deep learning supervised models usually require large and well annotated datasets, and developing such a dataset for the Peruvian Sign Language (PSL) \cite{lsp_2015} is expensive and difficult to achieve. Furthermore, in the same way as spoken languages, signs languages also present local variations e.g. people who live in Lima metropolitan area are not expected to use the same set of signs as people leaving in other parts of the country. A need exists for approaching this task with self-supervised learning or by means of weakly labeled data.

This article reports research conducted with the goal of proposing a method for detecting PSL signs using a weakly annotated dataset, and answering the following research questions:

\begin{enumerate}[(i)]
\item What are most relevant currently available techniques for training an AI model from  weakly annotated video and audio transcription?\label{q1}
\item How precise and exhaustive is the model described in the above question on the recognition of a reduced set of signs in a weakly annotated dataset?\label{q2}
\item What is the relation between the number of samples and the detection of new LSP elements in terms of nSDm precision and recall?\label{q3}
\end{enumerate}

The Pontifical Catholic University of Peru (PUCP) Grammar and  Signs research group created a PSL dataset \cite{lsp_dataset} that is weakly annotated because it does not show exactly the relation between the instant when a sign that is emitted and its corresponding translation.

>>>>

\title{%
	\vspace{-2.0cm}
	\textbf{Talking with signs} \\	
	\Large \textbf{A method for progressively detect sings in a non annotated Peruvian Sings Language corpus}
}

@@

\begin{abstract}
People with deafness or hearing disabilities who aim to use computer based systems relies on state of art video classification and human action recognition techniques that combine traditional movement pattern recognition and deep learning techniques. In this work we present a pipeline for semi automatic video annotation applied to a non annotated \textit{Peruvian Signs Language} (PSL) corpus along with a novel method for a progressive detection of PSL elements (nSDm). We produced a set of video annotations indicating signs appearances for a small set of nouns and numbers along with a \textit{labeled PSL dataset} (PSL dataset). A composite model obtained from the combination of a 2D CNN trained with movement patterns extracted from the PSL dataset using Lucas Kanade optical flow, and a RNN with LSTM cells trained with raw rgb frames extracted from the PSL dataset achieved XX precision and XX exhaustivity on sings classification, reporting state of art results over the PSL dataset. \\
\keywords{Video Classification, Human Actions Detection, Peruvian Signs Language, Optical Flow, 2D CNN, LSTM.}
\end{abstract}

\section{Introduction}\label{intro}
The World Health Organization (WHO) stated that 466 million people world wide have disabling hearing loss, estimating that by 2050 over 900 million people will have disabling hearing loss that will represent a global cost of 750 million dollars annually \cite{deafness_and_hearing_loss_2019}.

The Peruvian Institute of Informatics and Statistics (INEI) conducted a national disabilities survey with the objective of segmenting and acquire a better understanding about disabilities that affect the Peruvian population \cite{disabilities_survey_2012}, the results showed that 1.8\% of the Peruvian population suffer of at least partial when not permanent deafness or hearing limitations.

As of today, thanks to Deep Learning techniques for Computer Vision and Natural Language Processing, it is completely feasible to propose and design systems that are able to detect and transcribe sign languages elements improving in systems accessibility for people with physical limitations. Sings detection is usually a supervised learning task that requires a large and fully labeled dataset in order to achieve satisfactory results during model training and inference tasks. At the time  of writing this work there were no labeled data sets available for the PSL \cite{lsp_2015}, previous work was done by the \textit{Grammar and Signs research group of the Pontifical Catholic University of Peru (PUCP)} who created the first PSL corpus \cite{lsp_dataset}, this corpus is not annotated because there is no available metadata that describes signs being emitted and

  on annotating a Peruvian Sign Language (PSL) \cite{lsp_2015} a dataset, configuring an expensive and difficult task to achieve. The Pontifical Catholic University of Peru (PUCP) Grammar and  Signs research group created a non annotated PSL dataset \cite{lsp_dataset} because it does not show exactly the relation between the instant when a sign that is emitted and its corresponding translation.

Furthermore, in the same way as spoken languages, signs languages also present local variations e.g. people who live in Lima metropolitan area are not expected to use the same set of signs as people leaving in other parts of the country. A need exists for approaching this task with self-supervised learning or by means of weakly or nonexistent labeled data.

This work reports research conducted with the goal of proposing a method for detecting PSL elements using a not annotated dataset, and answering the following research questions:

\begin{enumerate}[(i)]
\item What are most relevant and currently available techniques for training an AI model from not annotated videos and audio transcription?\label{q1}
\item How precise and exhaustive is the model described in the above question on the recognition of a reduced set of signs in a not annotated dataset?\label{q2}
\item What is the relation between the number of samples and the detection of new LSP elements in terms of nSDm precision and recall?\label{q3}
\end{enumerate}
